%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Side Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Creator} % Affiliation/role
    {License Manager} % Organization/group
    {Salzburg, Austria} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created this tool on my on initiative to reduce manual workload.}
        \item {Learned about FP in javascript and how does React work with Redux.}
        \item {Used: Javascript(ES6), React, Redux, Node.js, Webpack, Babel, Gulp.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contributor} % Affiliation/role
    {Social Network for Programmers} % Organization/group
    {Warwick, UK} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Helped to develop website which used github api to connect users in social network.}
        \item {Learned about Nodejs and 0auth and JWT session management, basics about NoSQL databases.}
        \item {Used: Javascript, NodeJs, AngularJs, socket.io, mongoDb, Yeoman, Gulp.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {Games Top-list System} % Organization/group
    {Guildford, UK} % Location
    {2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a games top list site with advanced statistics collection and listing.}
        \item {Learned about advanced OOP(SOLID), Project structuring, Deployment techniques.}
        \item {Used: Laravel, MySQL, AngularJs, jQuery, Bootstrap, Rocketeer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Final year project} % Affiliation/role
    {Project Management tool} % Organization/group
    {Loughborough, UK} % Location
    {2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Simple Project management web application.}
        \item {Learned how does frameworks work (MVC, Seeding, Migrations, ORM, active records) including OOP.}
        \item {Used: PHP, Laravel, MySQL, jQuery, Bootstrap.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
